% All cited references including own publications: appearance controlled via the keyword me
\printbibliography[env=bibliographyNoReference, heading=bibintoc, title={\FTMlangLiteratureName}, category={cited}]%
\cleardoublepage%
\printbibliography[env=bibliographyNoReference, heading=bibintoc, title={\FTMlangLiteratureOwnName}, keyword={me}]

@article{Asdrubali2016,
abstract = {Efficient thermal insulating materials can significantly reduce energy consumption for both heating and cooling of buildings. When selecting an insulation material, however, it is important to consider other important aspects, such as acoustic performance, environmental impacts, effects on human health and costs of production. That is the reason why key research developments are recently achieved in the field of sustainable, highly efficient materials. Within this context, this paper deals with the thermal and acoustic performance and the environmental impact analysis of two kinds of corrugated multi-layer cardboard panels, usually applied in the packaging industry. Thermal analyses were conducted in order to measure the thermal conductivity by means of both an experimental campaign and numerical methods. The acoustic absorption coefficient and the transmission loss were experimentally determined by means of an impedance tube. Finally a Life Cycle Assessment of the considered panels was implemented and compared to the performance of other commonly used insulation materials. The main results of the study show that the cardboard-made panels usually applied for low-cost packaging present promising performance in terms of both acoustic and thermal insulation potential, i.e. of the same order of magnitude than high-performance commercialized products. The environmental impact evaluation also reveals an interesting behavior of the corrugated cardboard panels, which can by any means be considered as a promising recycled insulation material.},
author = {Asdrubali, F. and Pisello, A. L. and D'Alessandro, F. and Bianchi, F. and Fabiani, C. and Cornicchia, M. and Rotili, A.},
doi = {10.1016/j.buildenv.2015.09.003},
file = {:D$\backslash$:/LRZ Synch {\&} Share/TUM/Studium/Maschinenwesen/Bachelorarbeit/Literatur/Asdrubali et al.{\_}2016{\_}Experimental and numerical characterization of innovative cardboard based panels Thermal and acoustic performan(2).pdf:pdf},
issn = {03601323},
journal = {Building and Environment},
keywords = {Cardboard panels,Corrugated cardboard,Innovative panels,Life cycle assessment,Recycled materials,Sound insulation,Thermal insulation panels},
pages = {145--159},
publisher = {Elsevier Ltd},
title = {{Experimental and numerical characterization of innovative cardboard based panels: Thermal and acoustic performance analysis and life cycle assessment}},
url = {http://dx.doi.org/10.1016/j.buildenv.2015.09.003},
volume = {95},
year = {2016}
}